intro

### 2021-11-05 06_Paper/ER-ED/intro.Rmd
corrected typo

[...]
<!-- Als Überleitung: Maladaptive ER Strategien zu ER Flexibility -->
Implications of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between Neurotizism and depressive symptoms [@Yoon2013].
Also, meta-analytic evidence exists linking a number of ER strategies with psychological disorders [@Aldao2010].
The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
First, adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015]. 
For example, greater ER variability is related to reduced negative affect and therefore adaptive in daily life [@Blanke2020].
Second, strategies have to be chosen from the repertoire that are useful for goal achieving.
This selection of strategies is influenced by numerous facotrs.
For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction.

>>>>

<!-- Einführung ER -->
[...]
Implications of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between Neurotizism and depressive symptoms [@Yoon2013].
Also, meta-analytic evidence exists linking a number of ER strategies with psychological disorders [@Aldao2010].
The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
First, adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015]. 
For example, greater ER variability is related to reduced negative affect and therefore adaptive in daily life [@Blanke2020].
Second, strategies have to be chosen from the repertoire that are useful for goal achieving.
This selection of strategies is influenced by numerous factors.
For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction.
